Information Set Generation in Kriegspiel

### 2010-12-14 paper/paper.tex
Added code listing; saving work

\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,latexsym,graphicx}
\usepackage{fullpage}
\usepackage{url,hyperref}
\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit,shapes.geometric}
\usepgflibrary{shapes.geometric}
%\usepackage{ijcai09}

\pagestyle{empty}

@@

\newenvironment{proof}{\vspace{-0.15in}\noindent{\bf Proof:}}%
        {\hspace*{\fill}$\Box$\par}
\newenvironment{proofsketch}{\noindent{\bf Proof Sketch.}}%
        {\hspace*{\fill}$\Box$\par\vspace{4mm}}
\newenvironment{proofof}[1]{\smallskip\noindent{\bf Proof of #1.}}%
        {\hspace*{\fill}$\Box$\par}

@@

Figure~\ref{3depths}
\begin{figure}
\centering
%\begin{minipage}{.4\textwidth}
\includegraphics[width=0.7\textwidth]{plots/3depths.pdf}
%\end{minipage}
%\begin{minipage}{.4\textwidth}
\includegraphics[width=0.7\textwidth]{plots/3depths_nolog.pdf}
%\end{minipage}
\caption{3depths}
\label{3depths}
\end{figure}

@@

\begin{figure}
\begin{verbatim}
1. Pa2:a4 Pa7:a5 2. Pd2:d4 Pb7:b6 3. Bc1:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d3 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pd3:d4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Pa2:a4 Pb7:b6 3. Bc1:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:f4 Pb7:b6 3. Bf4:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pa2:a3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pa2:a4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pb2:b3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pc2:c3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pe2:e3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pe2:e4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pf2:f3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pf2:f4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pg2:g3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pg2:g4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ph2:h3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ph2:h4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:a3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:c3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:d3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:c1 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ke1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ng1:f3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ng1:h3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 
\end{verbatim}
\caption{Abbreviated output from example game.  Generating information sets for black after five turns by each player.
From this, black can infer that there is definitely a white bishop at g5 and a white pawn at d6.}
\label{abbrevoutput}
\end{figure}

\begin{figure}
\begin{verbatim}
19
Moves:

@@

**********************************************
R - B Q K B N R 
- - - P P - P P 
N P - p - P - - 
P - P - - - b - 
- - - - - - - - 
- - - - - - - n 
p p p - p p p p 
r n - q k b - r 
**********************************************
Solutions founds: 25
\end{verbatim}
\caption{Verbose output from example game.  Generating information sets for black after five turns by each player.
From this, black can infer that there is definitely a white bishop at g5 and a white pawn at d6.}
\label{verboseoutput}
\end{figure}
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,latexsym,graphicx}
\usepackage{fullpage}
\usepackage{url,hyperref}
\usepackage{subfig}
\usepackage{tikz}
\usepackage{examplep}
\usepackage{moreverb}
\usepackage{listings}
\lstset{language=C,numbers=left,basicstyle=\footnotesize,numberstyle=\footnotesize}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit,shapes.geometric}
\usepgflibrary{shapes.geometric}
%\usepackage{ijcai09}

@@

\newenvironment{mylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\scriptsize}
{\end{list}}

\newenvironment{mytinylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\scriptsize\texttt}
{\end{list}}
\newenvironment{proof}{\vspace{-0.15in}\noindent{\bf Proof:}}%
        {\hspace*{\fill}$\Box$\par}
\newenvironment{proofsketch}{\noindent{\bf Proof Sketch.}}%
        {\hspace*{\fill}$\Box$\par\vspace{4mm}}
\newenvironment{proofof}[1]{\smallskip\noindent{\bf Proof of #1.}}%
        {\hspace*{\fill}$\Box$\par}

@@

Figure~\ref{3depths}
\begin{figure}
\begin{minipage}{0.5\linewidth}
\centering
\includegraphics[width=\textwidth]{plots/3depths.pdf}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\centering
\includegraphics[width=\textwidth]{plots/3depthsnolog.pdf}
\end{minipage}
\caption{3depths}
\label{3depths}
\end{figure}

@@

\begin{figure}
\begin{mytinylisting}
1. Pa2:a4 Pa7:a5 2. Pd2:d4 Pb7:b6 3. Bc1:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d3 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pd3:d4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Pa2:a4 Pb7:b6 3. Bc1:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:f4 Pb7:b6 3. Bf4:g5 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pa2:a3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pa2:a4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pb2:b3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pc2:c3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pe2:e3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pe2:e4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pf2:f3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pf2:f4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pg2:g3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Pg2:g4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ph2:h3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ph2:h4 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:a3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:c3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Nb1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:d3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Qd1:c1 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ke1:d2 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ng1:f3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
1. Pd2:d4 Pa7:a5 2. Bc1:g5 Pb7:b6 3. Ng1:h3 Pc7:c5 4. Pd4:d5 Nb8:a6 5. Pd5:d6 Pf7:f6 \\
\end{mytinylisting}
\caption{Abbreviated output from example game.  Generating information sets for black after five turns by each player.
From this, black can infer that there is definitely a white bishop at g5 and a white pawn at d6.}
\label{abbrevoutput}
\end{figure}

%\begin{figure}
\begin{verbatim}
19
Moves:

@@

**********************************************
R - B Q K B N R 
- - - P P - P P 
N P - p - P - - 
P - P - - - b - 
- - - - - - - - 
- - - - - - - n 
p p p - p p p p 
r n - q k b - r 
**********************************************
Solutions founds: 25
\end{verbatim}
%\caption{Verbose output from example game.  Generating information sets for black after five turns by each player.
%From this, black can infer that there is definitely a white bishop at g5 and a white pawn at d6.}
%\label{verboseoutput}
%\end{figure}

\begin{figure}
%\begin{listing}
\begin{lstlisting}
void generateInformationSet(uint16_t* trueState, uint16_t* possState, bool whiteMove, 
	uint16_t* possHistory, uint16_t** levels, int depth)
{
  if (!samePawnTries(trueState, possState, whiteMove)) return;  
  if (!sameCheckStatus(trueState, possState, whiteMove)) return; 
  if (depth == maxdepth) { // Then we have found a solution
	nSolutions++; return; // Report solution
  }
  uint16_t newPossState[16]; 
  int nMoves = 0;
  generateAttemptableMoves(possState, whiteMove, levels[depth], nMoves,false);
  checkForCheck(possState, whiteMove, levels[depth], nMoves); // prunes if not equal
  assert (nMoves < NMOVES); //

  if (whitePerspective == whiteMove) { // move from perspective plyaer 
    SetMove& failures = failedMoves[depth];
    for (SetMove::const_iterator itr = failures.begin(); itr != failures.end(); ++itr) {
      uint16_t move = *itr ;
      if (!foundMatchingMove(move,levels[depth],nMoves)) {
        return; // Prune: one of my own failed moves is not attemptable in this state
      }
    }
    // We know exactly what the actual move was; make it
    uint16_t& actualMove = moveHistory[depth];
    if (!foundMatchingMove(actualMove,levels[depth],nMoves)) {
      return; // Prune (because the move that we know we made at this depth is not legal)
    }
    // Otherwise, recurse 
    applyMove(possState,newPossState,actualMove);
    possHistory[depth] = actualMove;
    generateInformationSet(newTrueState, newPossState, !whiteMove, 
      possHistory, levels, depth+1);
  } else { 
    // We are at a level in the search tree where 
    // we are considering the possible moves for the opponent.
    // We know the number of attempted illegal moves, but not which ones

    // Must be enough attemptable moves in the state to match the number of failed attempts
    unsigned nIllegalMoves = countIllegalMoves(levels[depth], nMoves);
    if (nIllegalMoves < failedMoves[depth].size()) {
	return; // Prune if not enough attemptable moves
    }
    // Now we want to try each possible move that is legally executable (not just attemptable) 
    for (int i = 0; i < nMoves; i++) {
      uint16_t& move = levels[depth][i];
      if (isLegal(move)) { // Obviously, we can only execute the moves that are actually legal from this state
        applyMove(possState,newPossState,move);
        possHistory[depth] = move;
        generateInformationSet(newTrueState, newPossState, !whiteMove, 
          possHistory, levels, depth+1);
      }
    }
  }
}
\end{lstlisting}
\caption{The heart of the information set generation algorithm.}
\label{codelisting}
\end{figure}

Figure~\ref{codelisting}
\end{document}
